Clustering/Orthofinder analysis

### 2022-02-21 analysis/Orthofinder.Rmd
add some more changes

```{r setup}
library(tidyverse)
library(cowplot)
theme_set(theme_cowplot())
library(RColorBrewer)
library(patchwork)
library(UpSetR)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

@@

```{r}
counts <- plyr::join_all(list(ara_count, posi_count, amphi_count, zmar_count, zmuel_count, lgibba_count, s_polyrhi_count, w_aus_count, rice_count), by='Orthogroup', type='left') 
names(counts) <- c('Orthogroup', 'A. thaliana', 'P. australis', 'A. antarctica', 'Z. marina', 'Z. muelleri', 'L. gibba', 'S. polyrhiza', 'W. australis', 'O. sativa')
counts
```

@@

```{r}
per_group_spec <-
  per_spec %>% mutate(group = case_when(
    name %in% c(
      'A. trichopada',
      'B. distachyon',
      'O. sativa',
      'P. patens',
      'P. trichocarpa',
      'S. moellendorffii',
      'A. thaliana',
      'T. parvula',
      'V. vinifera',
      'Z. mays'
    ) ~ 'Terrestrial',
    name %in% c(
      'C. reinhardtii',
      'L. gibba',
      'S. polyrhiza',
      'O. lucimarinus',
      'W. australis'
    ) ~ 'Aquatic',
    name %in% c('P. australis', 'Z. muelleri', 'Z. marina', 'A. antarctica') ~ 'Seagrasses'
  )) 
```

@@

```{r}
mylistgroup <- lapply(split(groupx, names(groupx)), unname) # yuck - ugly code to convert the named vector to a list
```

@@

>>>>

```{r setup}
library(tidyverse)
library(cowplot)
theme_set(theme_cowplot())
library(RColorBrewer)
library(wesanderson)
library(patchwork)
library(UpSetR)
library(ggVennDiagram)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

@@

```{r}
counts <- plyr::join_all(list(ara_count, posi_count, amphi_count, zmar_count, zmuel_count, lgibba_count, s_polyrhi_count, w_aus_count, rice_count), by='Orthogroup', type='left') 
names(counts) <- c('Orthogroup', 'A. thaliana', 'P. australis', 'A. antarctica', 'Z. marina', 'Z. muelleri', 'L. gibba', 'S. polyrhiza', 'W. australis', 'O. sativa')
head(counts)
```

@@

```{r}
per_group_spec <-
  per_spec %>% mutate(group = case_when(
    name %in% c(
      'A. trichopada',
      'B. distachyon',
      'O. sativa',
      'P. patens',
      'P. trichocarpa',
      'S. moellendorffii',
      'A. thaliana',
      'T. parvula',
      'V. vinifera',
      'Z. mays'
    ) ~ 'Terrestrials',
    name %in% c(
      'C. reinhardtii',
      'L. gibba',
      'S. polyrhiza',
      'O. lucimarinus',
      'W. australis'
    ) ~ 'Aquatics',
    name %in% c('P. australis', 'Z. muelleri', 'Z. marina', 'A. antarctica') ~ 'Seagrasses'
  )) 
```

@@

```{r}
mylistgroup <- lapply(split(groupx, names(groupx)), unname) # yuck - ugly code to convert the named vector to a list
mylistgroup <- lapply(mylistgroup, unique)
```

@@

OK now we need to do the GOenrichment for those three groups.

Let's also make an Venn plot, we have only three groups:
```{r}
p <- ggVennDiagram(mylistgroup, label_alpha=0) + 
  scale_fill_gradientn(colours=wes_palette("Zissou1", 100, type = "continuous")) + 
  theme(legend.position = "none")
```

```{r fig.width=10}
p
```

Nice!
